Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2020-05-28 paper.Rnw
Suggestions, comments on #6
Adam, here are some suggestions, but please check carefully and feel free to reject.

% \begin{table}
% \begin{tabular}{p{1in}p{1.5}p{2in}p{2in}}
% & Observational Study&Mediation Analysis &Principal Stratification\\
% \hline
% Research question & How does $H$ affect $Y$& What is the role of $Z$'s
%                                              effect on $H$ in its
%                                              effect on $Y$? & Does
%                                                               $Z$'s
%                                                               effect
%                                                               on $H$
%                                                               predict its
%                                                               effect
%                                                               on $Y$?\\

>>>>

In summary: there is much to recommend the observational study approach
if risks of confounding bias appear limited
(due to the availability of high-quality covariates, good reason to
believe variation in implementation is random or haphazard, or other
factors).
A wide variety of straightforward and transparent estimation techniques 
are available, such as the propensity score
matching illustrated here, optionally also including covariates in the 
outcomes model for additional protection against bias.
The result---the ATE of implementation on the outcome---is an
intuitive estimand.

Mediation analysis may have stronger standing where
at least one well-represented level of the implementation
variable is interpretable in the control condition.
In our example, $H=0$ included both low hint usage in
the treatment group and no access to hints in the control group.
When employed, mediation analysis can contextualize the estimated
implementation effect from the observational study in terms of the 
experiment's overall treatment
effect, enabling implementation to be interpreted as a causal
mechanism.

However, where unobserved confounding is a serious threat, and complex
statistical modeling (and model checking) is not a practical barrier,
PS may be a better choice because no ignorability assumptions are necessary.
% \begin{table}
% \begin{tabular}{p{1in}p{1.5}p{2in}p{2in}}
% & Observational Study&Mediation Analysis &Principal Stratification\\
% \hline
% Research question & How does $H$ affect $Y$& What is the role of $Z$'s
%                                              effect on $H$ in its
%                                              effect on $Y$? & Does
%                                                               $Z$'s
%                                                               effect
%                                                               on $H$
%                                                               predict its
%                                                               effect
%                                                               on $Y$?\\
